Multi-level modeling with Openflexo/\FML - A contribution to the \mpc

### 2021-05-31 8-discussion.tex

  Due to the level-agnostic aspect of our approach, we could insert a new
  level, for example. It would consist in creating new concepts we would link
  to other ones. Then, we would add any necessary constraints on those concepts
  and on the relationships linking them to the other existing concepts. This type of change can be easily done.

  On the other hand, making changes to the existing models could be difficult. For example, given a requirement, an instance cannot be changed into a concept easily. In the context of the process described in the challenge, this could

  Design Task ->

>>>>

  Due to the level-agnostic aspect of our approach, we could insert a new
  level, for example. It would consist in creating new concepts we would link
  to other ones. Then, we would add any necessary constraints on those concepts
  and on the relationships linking them to the other existing concepts. This type 
  of change can be easily done. On the other hand, making changes to the existing 
  models could be difficult. For example, given a requirement, an instance cannot 
  be changed into a concept easily. This case could occur if the challenge had 
  refined the specification by requiring specific design tasks. In this context, 
  we would have to transform \emph{Design Task} into a concept whose instances 
  could have been "using agile methodology".
